Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-03-02 manuscripts/paper-1/main.tex
New image added

    The notion of the digital twin, which has gained popularity in 
    recent years, is often subject to vague and ambiguous envisions\cite{Review1}.
    The mispresenting this notion began with the physical twin of the Apollo 13 spacecraft. 
    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilised in the physical simulations. 
    Even though the digital aspect was expected to be present, there wasn't\cite{GrievesApollo13}.
    Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
    which was used simultaneously before and during operation, can be argued to be similar. 
    The board was a twin of the operation, and it included model of battalions and ships that reflected the actual 
    locations of the corresponding formations. Furthermore, synchronisation was 
    implemented to give directives from the real system to control the operation 
    flow and to update the physical twin state\cite{AMRC}.
    In contrast, a digital twin is a virtual counterpart of a real system, which should 
    be synchronized with a selected frequency and fidelity\cite{Review1,Review2,digitaltwinconsortium2022}.

    The envision of digital twin emerged from Grieves'es conceptual model, which was called mirrored spaces model in 2002~\cite{Originsofdigitaltwinconcept},
    and later referenced in 2005 journal article~\cite{2005JournayArticle}. 
    Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
    The goal was to gather as much as  information about the real system to minimize the waste of system's sources such as energy, 
    time and material. Initially this model had four main parts with real system, 
    virtual system, connection between the real and virtual system and virtual simulations\cite{GrievesPLMBook}. 
    Later, Grieves removed the latter, in order to simplify the model\cite{Originsofdigitaltwinconcept}.Furthermore, after co-authoring with the Vicker's in 2010, 
    Grieves decided to use the NASA invented Digital Twin word, instead of information mirroring model\cite{Originsofdigitaltwinconcept}.

@@

    FELICE is a complex system which  addresses a critical problem in robotics which is the effective integration of human and robot abilities in a collaborative setting. 
    This challenge requires the development of sophisticated algorithms and techniques that facilitate seamless communication, cooperation, and coordination between humans and robotic agents. 
    By addressing this issue, FELICE tries to represent a significant advancement in the field of robotics and has the potential to enhance the effectiveness and efficiency of a wide range of 
    human-robot collaborative tasks with the consideration of safety~\cite{FELICE}.

    Main purpose of this study is to identify the quality attributes and inspect several artifacts 
    with these to evaluate the quality of the digital twin for the FELICE project, 
    which is currently in the design phase~\cite{FELICE}. These artifacts included process videos showing the current 
    assembly procedure, a scope definition, a requirements specification, a general and operational conceptual model, 
    and a discrete event simulation module. We assessed the quality of these artifacts based on five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.

@@

    \section{State of the art on quality}
    Oxford English Dictionary describes the word quality  either as a noun or as an adjective. 
    The adjective form indicates, a high standard or excellence. For example, the phrase quality products implies 
    that quality adds a high standard state to the product. There are several definitions which describes a quality 
    as a noun,however the impactful definition is the quality as a standard of an entity which is measured against the 
    different or the similar entities\cite{OxfordDictionary}.This definition clearly shows the relativity of quality.In addition, quality be defined 
    as the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.    
    \subsection{Product quality and Management}
    A product is a tangible or intangible system that satisfies the needs or wants of a customer. It could be a physical system like a car, or an abstract system, like a digital twin. 
    Regarding product quality, there are two different aspects~\cite{GrievesPLMBook}.
    First, quality is an attribute of a product, which meets product specifications. Specifications are mostly defined by the supra-systems subsystems, such as by the stakeholders within the supra-system,  If the stakeholders' expectations, or needs, are met, we can consider high quality.
    The ability to execute to a specific usage standard is the second facet of product quality. Since this standardization is usually not controllable, unlike the first, the system's quality will be determined by how the implied or obligatory standards are fulfilled.

    Quality management is a management type, which has an interest in Quality, and quality assurance is one of the parts of quality management, 
    which focuses on providing fidelity that quality requirements will be fulfilled. This means that quality assurance is a subsystem of quality management.

    Quality management systems(QMS) are functioning to plan and execute the organizations quality policies and goals. 
    Examples of such systems can be a standard like ISO 9001 which can provide a framework for an organization, or a data-driven methodology such  as Six-Sigma to reduce defects and improve efficiency. 
    This concepts  are not new, for example ISO 9001 standard has been established in 1987, and still being regularly updated ~\cite{ISO90012015}. 
    \subsection{Software quality}
    Software is a combination of programs and data which can be used by the virtual 
    systems as well as  a physical system like a computer system. In contrast a hardware 
    is a physical subsystem of a computer system\cite{OxfordDictionary}.

    Software Quality is determined by how well software fulfill the requirements that were set. However, those requirements  
    not always reflect what the stakeholders actually need, hence the quality depends how accurately this requirements were set \cite{IEE730-2014}. 
    As a result, functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability 
    and portability are the standartized  eight attributes that measure software quality \cite{ISO/IEC:25010}.

    Software quality management techniques comes from already used manufacturing techniques in the  industries. For example the  product quality assurance has been used as a software quality management activity with some modifications. For example, in the manufacturing, products will never exactly meet a specification, due to errors in the machining which results in some tolerance area. But in the software systems, or more precise in the virtual systems, it's most of the time not the case. Also its nearly imposible to conclude that, 
    the software product is fully meet its speficiations. 
    Hence, most of the quality assesments are subjective process and as a result, the quality attributes should be inspected subjectively \cite{SoftwareEngineering}.

    \subsection{Simulation Quality}
    Simulation models are not merely virtual systems; they are also abstracted systems, 
    which are nothing more than imitations or, to be more precise, abstractions of the real systems. 
    In fact, everyday, simulation of the real systems occurs in the human brain when prediction of the future outcome or  about the 
    past state of some occured event required\cite{MobusSystemTheory}. However, most of the simulation processeses are computer 
    based with software programs. Consequently, the idea of simulation software programs emerges. 
    For example, ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} are examples of these simulation software programs.

    Validation and verification is used to evaluate the quality characteristics of the simulation 
    model \cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
    Validation is the process of evaluating the simulation quality of the model in comparison to 
    the real system from the perspective of the model's intended applications.
    On the other hand, verification is a procedure to 
    evaluate a simulation model's implementation and its associated 
    data concerning the conceptual description and specifications of the 
    model developer\cite{StewartSimulation,VerificationValidationSergent}.

@@

    The first level of filtering for the literature review on digital twin publications involves specific criteria. These include that dissertations must be written in English and 
    published in a journal or conference, and that the search term must be an exact match. To execute this initial filtration, 
    the following queries are used for Google Scholar and Scopus respectively: "search term" and ALL ("digital twin quality") AND (LIMIT-TO (LANGUAGE, "English")).

@@

    The search for "digital twin verification" initially resulted in 19 hits on Google Scholar and none on Scopus. 
    After the second level of filtering, one duplicate dissertation was removed and two dissertations that were not in 
    English were also eliminated. As a result, all dissertations were rejected.

@@

    After a thorough review of 17 research papers, a number of significant findings were revealed.

    First, it was noted that Shcherba et al.  focus on the importance of model quality as an observation for a digital twin subsystem. 
    However, they acknowledged that the quality assessment of the digital twin cannot solely rely on models~\cite{Shcherba}.

@@

    Overall, these studies provide valuable insights into various aspects of digital twin quality assessment, 
    including model consistency, stability, and validation, as well as machine learning-based approaches and real-time anomaly detection. 
    However, the identified open problems, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes, 
    call for further research in the field to improve the quality and reliability of digital twins. Moreover, 
    the lack of well-defined quality parameters for digital twins poses a significant challenge in ensuring their quality,
    which necessitates the development of appropriate quality metrics and standards for digital twins.
    \subsection{Digital Twin Quality Attributes}
    We consolidated our findings from various standards, including ISO/IEC:25010, IEE730-2014, ISO9000, ISO9001, as well as consulted the  Oxford dictionary to synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014,OxfordDictionary}.

    \textbf{Correctness} is a  derived word from the adjective correct, which means that something is error-free in regard to fact or truth. In the context of the digital twins, our fact or truth is a real system hence, correctness is a grade of quality, that indicates an error between the real system and a digital twin system.
    Meanwhile, the quality of being correct is described by the term accuracy \cite{OxfordDictionary}.

    \textbf{Completeness} is a derived word from the word complete, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
    The adjectival form of complete is a state of having all the neccesary or appropriate parts\cite{OxfordDictionary}.

    \textbf{Fidelity}
    Fidelity refers to the degree of exactness with which the real system is copied and represented.Low-fidelity indicates a simplified representation, 
    while high-fidelity refers to an accurate and detailed representation of the real system \cite{Review2}. 
    The concept of fidelity has garnered significant attention in recent years and continues to be an important area of research in digital twins\cite{Review2}\cite{Review1}.

    \textbf{Efficiency}
    Efficiency refers to the  quality of  being efficient, and efficient is achieving
    maximum productivity with minimum wasted effort or expense. The concept of efficiency is tightly coupled to productivity, which  refers to a quality of being productive,
    also  the word productive can be explained as producing or able to produce large amounts of goods\cite{OxfordDictionary}.  
    For example time efficiency indicates that,  with the less amount of time as an input, more output with the minimum 
    waste during the process is desired . Goods of the  digital twin is nothing but an information, which Grieves first 
    indicated with this Information Mirror Model\cite{GrievesPLMBook}.

@@

    \textbf{Process Videos:}
    Project partner provided three videos initially to explain the manual assembly procedures performed at each of the three workstations. From the videos,  
    the sequence of assembly steps were extracted  at least for one product variant. The tools and the parts needed for each assembly operation was observed. Additionally, an approximate duration of each assembly step were estimated, and some ergonomic characteristics of each operation was derived. 
    The derivable ergonomic characteristics mainly included the poses and motions performed by the operators.

    \textbf{Scope Definition:}
    To better understand the context and focus of the digital twin, 
    project partner used a methodology based on hierarchical task analysis and the process videos. 
    This resulted in a scope definition that identified entities to be twinned, entities to be tracked, and important areas in the scene. 
    Entities to be twinned needed to be represented accurately in the simulation models, including their position, pose, speed, fatigue, and other state variables. 
    Entities to be tracked, on the other hand, only required position information. The scope definition was based on a floor plan of the production facility, with the three workstations marked as gray rectangles. 
    The human workers, cobot, and adaptive workstation were identified as entities to be twinned, and therefore required accurate representation, 
    monitoring, and simulation. Other entities, such as an AGV, carts with doors, and screwdrivers used for assembly operations, were designated as entities to be tracked.

@@

    \textbf{Conceptual Model} was comprised of two parts:  a general conceptual model and an operational conceptual model. Both models provided a description of the assembly line processes, but the operational conceptual model focused on the specific steps of the assembly process, while the general conceptual model focused on higher-level processes and workflows.
    The general conceptual model was represented using a general flow chart notation that distinguished between a root node, activity nodes, and decision nodes.
    The operational conceptual model consisted of three spreadsheets, each displaying the sequence of assembly operations performed at one workstation. 
    The assembly operations were divided into macro- and micro-operations, with each macro-operation referring 
    to one part of the final product being assembled, and the micro-operations referring to the individual steps needed to complete the respective macro-operation.

@@

    \subsection{Manual Artifact Reviews and Evoluation}
    During the initial stages of the project, when the target system was not yet available, there was a lack of observable data about system behavior that could be utilized for validation. 
    Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon. Therefore, manual reviews were deemed the most suitable tool to account for the characteristics of this situation. Manul review inclueded, audits, inspections, reviews, structural analysis 
    and walkthroughs with the project partners which was inspiered from the Balci's manual review works \cite{balcitechniques}. Lastly, identified issuess after the reviews were mapped to the quality attributes.

@@

    \begin{figure}[htbp]
        \includegraphics[scale=0.75]{quality_inspection_results.png}
        \caption{Overall Quality Inspection Results}
        \label{fig:QualityInspectonResults}
    \end{figure}\begin{figure}[htbp]
        \includegraphics[scale = 0.45]{quality_inspection_results_with_artifacts.png}
        \caption{ Quality Inspection Results Categorized with Artifacts}
        \label{fig:QualityInspectonResultsWithArtifacts}
    \end{figure}
    \subsection{Manual Review Result}
    \subsection{Quality Inspection with Quality Attributes}
    As can be seen in Figures ~\ref{fig:QualityInspectonResults} and ~\ref{fig:QualityInspectonResultsWithArtifacts}, based on our inspection of the given artifacts,
    we have identified a total of seven correctness issues, eleven completeness issues, and two fidelity issues. 
    It is important to note that we were unable to inspect for efficiency as the project is still in the design phase, 
    and we do not have enough data to make estimations for this attribute. Additionally, all of our inspections were conducted manually, 
    which is susceptible to human error and inspector bias.
    \section{Discussion}
    \label{section:framework_1}
    To mitigate potential human bias and enhance the data-driven approach for quality assurance, ongoing research aims to address these issues. 
    Furthermore, the assessment of digital twin quality can be significantly improved by obtaining data from real systems, thereby enabling better visibility and a more robust evaluation. As such, the use of empirical data in combination with machine learning techniques can offer a more objective and reliable means of evaluating the correctness, completeness, fidelity, efficiency, and evolvability of digital twins. Additionally, given the manual nature of the current inspections, it is important to acknowledge the potential for inspector bias, which may impact the accuracy of the assessments. 
    By leveraging technology to automate certain aspects of the evaluation process, it is possible to reduce the potential for such biases and improve the overall quality of digital twin assessments.

>>>>

    The notion of the digital twin, which has gained popularity in 
    recent years, is often subject to vague and ambiguous envisions\cite{Review1}.
    The mispresenting of this notion began with the physical twin of the Apollo 13 spacecraft. 
    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in physical simulations. 
    Even though the digital aspect was expected to be present, there wasn't\cite{GrievesApollo13}.
    Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
    which was used simultaneously before and during the operation, and can be argued to be similar. 
    The board was a twin of the operation, and it included models of battalions and ships that reflected the actual 
    locations of the corresponding formations. Furthermore, synchronization was 
    implemented to give directives from the real system to control the operation 
    flow and to update the physical twin state\cite{AMRC}.
    In contrast, a digital twin is a virtual counterpart of a real system, which should 
    be synchronized with a selected frequency and fidelity\cite{Review1,Review2,digitaltwinconsortium2022}.

    The envision of a digital twin emerged from Grieves'es conceptual model, which was called mirrored spaces model in 2002~\cite{Originsofdigitaltwinconcept},
    and later referenced in a 2005 journal article~\cite{2005JournayArticle}. 
    Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
    The goal was to gather as much information about the real system to minimize the waste of the system's sources such as energy, 
    time and material. Initially, this model had four main parts of a real system, 
    virtual system, connection between the real and virtual system and virtual simulations\cite{GrievesPLMBook}. 
    Later, Grieves removed the latter, to simplify the model\cite{Originsofdigitaltwinconcept}. Furthermore, after co-authoring with Vicker in 2010, 
    Grieves decided to use the NASA-invented Digital Twin word, instead of the information mirroring model\cite{Originsofdigitaltwinconcept}.

@@

    FELICE is a complex system that addresses a critical problem in robotics which is the effective integration of human and robot abilities in a collaborative setting. 
    This challenge requires the development of sophisticated algorithms and techniques that facilitate seamless communication, cooperation, and coordination between humans and robotic agents. 
    By addressing this issue, FELICE tries to represent a significant advancement in the field of robotics and has the potential to enhance the effectiveness and efficiency of a wide range of 
    human-robot collaborative tasks with the consideration of safety~\cite{FELICE}.

    The main purpose of this study is to identify the quality attributes and inspect several artifacts 
    with these to evaluate the quality of the digital twin for the FELICE project, 
    which is currently in the design phase~\cite{FELICE}. These artifacts included process videos showing the current 
    assembly procedure, a scope definition, a requirements specification, a general and operational conceptual model, 
    and a discrete event simulation module. We assessed the quality of these artifacts based on five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.

@@

    \section{State of the art on quality}
    Oxford English Dictionary describes the word quality either as a noun or an adjective. 
    The adjective form indicates, a high standard or excellence. For example, the phrase quality products imply 
    that quality adds a high standard state to the product. Several definitions describe quality 
    as a noun, however, the impactful definition is the quality as a standard of an entity which is measured against the 
    different or the similar entities\cite{OxfordDictionary}. This definition clearly shows the relativity of quality. In addition, quality is defined 
    as the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.    
    \subsection{Product quality and Management}
    A product is a tangible or intangible system that satisfies the needs or wants of a customer. It could be a physical system like a car, or an abstract system, like a digital twin. 
    Regarding product quality, there are two different aspects~\cite{GrievesPLMBook}.
    First, quality is an attribute of a product, which meets product specifications. Specifications are mostly defined by the supra-systems subsystems, 
    such as by the stakeholders within the supra-system,  If the stakeholders' expectations, or needs, are met, we can consider high quality.
    The ability to execute to a specific usage standard is the second facet of product quality. Since this standardization is usually not controllable, 
    unlike the first, the system's quality will be determined by how the implied or obligatory standards are fulfilled.

    Quality management systems(QMS) function to plan and execute the organization's quality policies and goals. 
    Examples of such systems can be a standard like ISO 9001 which can provide a framework for an organization, or a data-driven methodology such as Six Sigma to reduce defects and improve efficiency. 
    These concepts are not new, for example, ISO 9001 standard has been established in 1987, and is still being regularly updated ~\cite{ISO90012015}. 
    \subsection{Software quality}
    Software is a combination of programs and data which can be used by virtual 
    systems as well as a physical system like a computer system. In contrast, hardware 
    is a physical subsystem of a computer system\cite{OxfordDictionary}.

    Software Quality is determined by how well software fulfills the requirements that were set. However, those requirements  
    not always reflect what the stakeholders need, hence the quality depends on how accurately these requirements were set \cite{IEE730-2014}. 
    As a result, functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability 
    and portability is the standardized eight attributes that measure software quality \cite{ISO/IEC:25010}.

    Software quality management techniques come from already used manufacturing techniques in the industries. For example, product quality assurance has been used as a 
    software quality management activity with some modifications. For example, in manufacturing, products will never exactly meet a specification, due to errors in the machining which results in some tolerance area. 
    But in the software systems, or more precisely in the virtual systems, it's most of the time, not the case. Also, it's nearly impossible to conclude that, 
    the software product fully meets its specifications. 
    Hence, most of the quality assessments are subjective processes and as a result, the quality attributes should be inspected subjectively \cite{SoftwareEngineering}.

    \subsection{Simulation Quality}
    Simulation models are not merely virtual systems; they are also abstracted systems, 
    which are nothing more than imitations or, to be more precise, abstractions of real systems. 
    Every day, simulation of the real systems occurs in the human brain when the prediction of the future outcome or about the 
    past state of some occurred event required\cite{MobusSystemTheory}. However, most of the simulation processes are computer-based with software programs. Consequently, the idea of simulation software programs emerges. 
    For example, ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} are examples of these simulation software programs.

    Validation and verification are used to evaluate the quality characteristics of the simulation 
    model \cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
    Validation is the process of evaluating the simulation quality of the model in comparison to 
    the real system from the perspective of the model's intended applications.
    On the other hand, verification is a procedure to 
    evaluate a simulation model's implementation and its associated 
    data concerning the conceptual description and specifications of the 
    model developer\cite{StewartSimulation,VerificationValidationSergent}.

@@

    The first level of filtering for the literature review on digital twin publications involves specific criteria. These include that dissertation must be written in English and 
    published in a journal or conference and that the search term must be an exact match. To execute this initial filtration, 
    the following queries are used for Google Scholar and Scopus respectively: "search term" and ALL ("digital twin quality") AND (LIMIT-TO (LANGUAGE, "English")).

@@

    The search for "digital twin verification" initially resulted in 19 hits on Google Scholar and none on Scopus. 
    After the second level of filtering, one duplicate dissertation was removed and two dissertations that were not in 
    English was also eliminated. As a result, all dissertations were rejected.

@@

    After a thorough review of 17 research papers, several significant findings were revealed.

    First, it was noted that Shcherba et al. focuses on the importance of model quality as an observation for a digital twin subsystem. 
    However, they acknowledged that the quality assessment of the digital twin cannot solely rely on models~\cite{Shcherba}.

@@

    Overall, these studies provide valuable insights into various aspects of digital twin quality assessment, 
    including model consistency, stability, and validation, as well as machine learning-based approaches and real-time anomaly detection. 
    However, the identified open problems, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes, 
    call for further research in the field to improve the quality and reliability of digital twins. Moreover, 
    the lack of well-defined quality parameters for digital twins poses a significant challenge in ensuring their quality,
    which necessitates the development of appropriate quality metrics and standards for digital twins.
    \subsection{Digital Twin Quality Attributes}
    We consolidated our findings from various standards, including ISO/IEC:25010, IEE730-2014, ISO9000, and ISO9001, as well as consulted the  Oxford dictionary to 
    synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014, OxfordDictionary}.

    \textbf{Correctness} is a  derived word from the adjective correct, which means that something is error-free regarding fact or truth. In the context of the digital twins, our fact or truth is a real system hence, correctness is a grade of quality, that indicates an error between the real system and a digital twin system.
    Meanwhile, the quality of being correct is described by the term accuracy \cite{OxfordDictionary}.

    \textbf{Completeness} is a derived word from the word complete, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
    The adjectival form of complete is a state of having all the necessary or appropriate parts\cite{OxfordDictionary}.

    \textbf{Fidelity}
    Fidelity refers to the degree of exactness with which the real system is copied and represented. Low fidelity indicates a simplified representation, 
    while high-fidelity refers to an accurate and detailed representation of the real system \cite{Review2}. 
    The concept of fidelity has garnered significant attention in recent years and continues to be an important area of research in digital twins\cite{Review2}\cite{Review1}.

    \textbf{Efficiency}
    Efficiency refers to the quality of being efficient, and efficiency is achieving
    maximum productivity with minimum wasted effort or expense. The concept of efficiency is tightly coupled to productivity, which refers to the quality of being productive,
    also the word productive can be explained as producing or being able to produce large amounts of goods\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum 
    waste during the process is desired. Goods of the digital twin are nothing but information, which Grieves first 
    indicated with this Information Mirror Model\cite{GrievesPLMBook}.

@@

    \textbf{Process Videos:}
    The project partner provided three videos initially to explain the manual assembly procedures performed at each of the three workstations. From the videos,  
    the sequence of assembly steps was extracted at least for one product variant. The tools and the parts needed for each assembly operation were observed. Additionally, the approximate duration of each assembly step 
    was estimated, and some ergonomic characteristics of each operation were derived. 
    The derivable ergonomic characteristics mainly included the poses and motions performed by the operators.

    \textbf{Scope Definition:}
    To better understand the context and focus of the digital twin, 
    the project partner used a methodology based on hierarchical task analysis and the process videos. 
    This resulted in a scope definition that identified entities to be twinned, entities to be tracked, and important areas in the scene. 
    Entities to be twinned needed to be represented accurately in the simulation models, including their position, pose, speed, fatigue, and other state variables. 
    Entities to be tracked, on the other hand, only required position information. The scope definition was based on a floor plan of the production facility, with the three workstations marked as gray rectangles. 
    The human workers, cobot, and adaptive workstation were identified as entities to be twinned, and therefore required accurate representation, 
    monitoring, and simulation. Other entities, such as an AGV, carts with doors, and screwdrivers used for assembly operations, were designated as entities to be tracked.

@@

    \textbf{Conceptual Model} was comprised of two parts:  a general conceptual model and an operational conceptual model. Both models described the assembly line processes, but the operational conceptual model focused on the specific steps of the assembly process, while the general conceptual model focused on higher-level processes and workflows.
    The general conceptual model was represented using a general flow chart notation that distinguished between a root node, activity nodes, and decision nodes.
    The operational conceptual model consisted of three spreadsheets, each displaying the sequence of assembly operations performed at one workstation. 
    The assembly operations were divided into macro- and micro-operations, with each macro-operation referring 
    to one part of the final product being assembled, and the micro-operations referring to the individual steps needed to complete the respective macro-operation.

@@

    \subsection{Manual Artifact Reviews and Evoluation}
    During the initial stages of the project, when the target system was not yet available, there was a lack of observable data about system behavior that could be utilized for validation. 
    Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon. Therefore, manual reviews were deemed the most suitable tool to account for the characteristics of this situation.
    The manual review included, audits, inspections, reviews, structural analysis 
    and walkthroughs with the project partners which was inspired by Balci's manual review works \cite{balcitechniques}. Lastly, identified issues after the reviews were mapped to the quality attributes.

@@

    \begin{figure}[htbp]
        \includegraphics[scale = 0.40]{quality_inspection_results_with_artifacts.png}
        \caption{ Quality Inspection Results Categorized with Artifacts}
        \label{fig:QualityInspectonResultsWithArtifacts}
    \end{figure}

    \subsection{Manual Review Result}
    \subsection{Quality Inspection with Quality Attributes}
    As can be seen in Figures and ~\ref{fig:QualityInspectonResultsWithArtifacts}, based on our inspection of the given artifacts,
    we have identified a total of seven correctness issues, eleven completeness issues, and two fidelity issues. 
    It is important to note that we were unable to inspect for efficiency as the project is still in the design phase, 
    and we do not have enough data to make estimations for this attribute. Additionally, all of our inspections were conducted manually, 
    which is susceptible to human error and inspector bias.
    \section{Discussion}
    \label{section:framework_1}
    To mitigate potential human bias and enhance the data-driven approach for quality assurance, ongoing research aims to address these issues. 
    Furthermore, the assessment of digital twin quality can be significantly improved by obtaining data from real systems, thereby enabling better visibility and a more robust evaluation. As such, the use of empirical data in combination with machine learning techniques can offer a more objective and reliable means of evaluating the correctness, completeness, fidelity, efficiency, and evolvability of digital twins. Additionally, given the manual nature of the current inspections, it is important to acknowledge the potential for inspector bias, which may impact the accuracy of the assessments. 
    By leveraging technology to automate certain aspects of the evaluation process, it is possible to reduce the potential for such biases and improve the overall quality of digital twin assessments.
